---
title: XXX
documentclass: article
date: "`r format(Sys.Date(),'%d %B, %Y')`"
output:
  pdf_document: 
    df_print: paged
    fig_caption: yes
    highlight: tango
    number_sections: yes
    citation_package: natbib
    keep_tex: yes
bibliography: library.bib
author: | 
  XXX
header-includes: 
  \usepackage{amsmath} 
  \usepackage[utf8]{inputenc} 
  \usepackage{autobreak}   
  \usepackage{setspace}
  \doublespacing
  \usepackage{hyperref} 
  \usepackage[authoryear]{natbib} 
  \usepackage{caption} 
  \usepackage{babel} 
  \usepackage{multirow}
  \usepackage{pdflscape}
  \usepackage{rotating, graphicx}
  \usepackage{dcolumn}
geometry: margin=1in
BottomRFooter: \footnotesize Page \thepage\
addtoprule: yes
addfootrule: yes
bottom: 2
top: 2
one_column: yes
skip_final_break: yes
watermark: no
HardSet_layout: yes
RemovePreprintSubmittedTo: no
Journal: Energy Economics
toc: yes
fontsize: 12pt
linestretch: 2
link-citations: yes
links-as-notes: true
abstract: |
  This paper examines  
acknowledgements: "This work would not have been possible without the excellent \n"
keywords: "Multivariate VAR DCC GARCH"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r ,echo=FALSE, results='asis', warning=FALSE, message=FALSE}

##################### FOR OLS OUTPUT #########################################

library("stargazer")

pre <- read.csv(file.choose()) 
names(pre) <- c("abc vs XXXXX XXXX Contract 01", "abc vs XXXXX XXXX Contract 02", "abc vs XXXXX XXXX Contract 03","abc vs XXXXX XXXX Contract 04","Date","SI", "OI") 

post <- read.csv(file.choose())
names(post) <-  c("abc vs XXXXX XXXX Contract 01", "abc vs XXXXX XXXX Contract 02", "abc vs XXXXX XXXX Contract 03","abc vs XXXXX XXXX Contract 04","Date","SI", "OI")

# OLS: conditional correlation ~ SI + OI

#pre
pre.ols.sp01SIOI <- lm(`abc vs XXXXX XXXX Contract 01`~ SI + OI, data=pre)
pre.ols.sp02SIOI <- lm(`abc vs XXXXX XXXX Contract 02`~ SI + OI, data=pre)
pre.ols.sp03SIOI <- lm(`abc vs XXXXX XXXX Contract 03`~ SI + OI, data=pre)
pre.ols.sp04SIOI <- lm(`abc vs XXXXX XXXX Contract 04`~ SI + OI, data=pre)

#post
post.ols.sp01SIOI <- lm(`abc vs XXXXX XXXX Contract 01`~ SI + OI, data=post)
post.ols.sp02SIOI <- lm(`abc vs XXXXX XXXX Contract 02`~ SI + OI, data=post)
post.ols.sp03SIOI <- lm(`abc vs XXXXX XXXX Contract 03`~ SI + OI, data=post)
post.ols.sp04SIOI <- lm(`abc vs XXXXX XXXX Contract 04`~ SI + OI, data=post)

stargazer(pre.ols.sp01SIOI,pre.ols.sp02SIOI,pre.ols.sp03SIOI,pre.ols.sp04SIOI,post.ols.sp01SIOI,post.ols.sp02SIOI,post.ols.sp03SIOI,post.ols.sp04SIOI, style = "qje", header=FALSE,align =TRUE, title = "Regression Analysis between Conditional Correlation, Speculation Index and Open Interest" )

```


#### Error 

when float.env = "sidewaystable" is used even though in YAML package is included 

output file: stargazer_issue.knit.md
! LaTeX Error: File `sidewaystable.sty' not found.

! Emergency stop.
<read *> 

Error: LaTeX failed to compile stargazer_issue.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips. See stargazer_issue.log for more info.
Execution halted

#### when same code in run under the project file error is as follows

output file: Paper1.v7_11Jun2020.knit.md

This is pdfTeX, Version 3.14159265-2.6-1.40.21 (MiKTeX 2.9.7440 64-bit)
entering extended mode
I was unable to find any missing LaTeX packages from the error log Paper1.v7_11Jun2020.log.
This is pdfTeX, Version 3.14159265-2.6-1.40.21 (MiKTeX 2.9.7440 64-bit)
entering extended mode
I was unable to find any missing LaTeX packages from the error log Paper1.v7_11Jun2020.log.
Error: LaTeX failed to compile Paper1.v7_11Jun2020.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips.
In addition: Warning messages:
1: In readLines(log) : line 884 appears to contain an embedded nul
2: In readLines(log) :
  incomplete final line found on 'Paper1.v7_11Jun2020.log'
3: In readLines(log) : line 884 appears to contain an embedded nul
4: In readLines(log) :
  incomplete final line found on 'Paper1.v7_11Jun2020.log'
5: In readLines(log) : line 884 appears to contain an embedded nul
6: In readLines(log) :
  incomplete final line found on 'Paper1.v7_11Jun2020.log'
Execution halted*

#### if using 
$\backslash$newpage $\backslash$blandscape $\backslash$elandscape then getting following error


! Undefined control sequence.
l.86 $\backslash$blandscape

Error: LaTeX failed to compile stargazer_issue.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips. See stargazer_issue.log for more info.
Execution halted




